My title

### 2024-03-12 paper/paper.qmd
changed modelsummary and apendix
changed apendix and modelsummary

$y_i|\mu_i$, $\sigma \sim \mbox{Normal}(\mu_i, \sigma)$

$\mu_i = \alpha + \phi_i$

@@

$y_i|\mu_i$, $\sigma \sim \mbox{Normal}(\mu_i, \sigma)$

$\mu_i = \alpha + \beta_i + \gamma_i$

@@

We expect a net negative relationship between the net efforts made by the helpline staff (Recorded by the Total_Coded column) and homeless death count, which implies that net effect of helpline calls **reduces** homeless death count in Toronto.

@@

modelsummary::modelsummary(
  list(
    "Total Coded Model" = total_coded_model
  ),
  statistic = "mad",
  fmt = 3
)
```

@@

modelsummary::modelsummary(
  list(
    "Referred and Informed Model" = referred_informed_model
  ),
  statistic = "mad",
  fmt = 3
)
```

>>>>

$y_i|\lambda_i$, $\sigma \sim \mbox{Poisson}(\lambda_i)$

$lambda_i = \alpha + \phi_i$

@@

$y_i|\mu_i$, $\sigma \sim \mbox{Poisson}(\lambda_i)$

$\lambda_i = \alpha + \beta_i + \gamma_i$

@@

We expect a net negative relationship between the net efforts made by the helpline staff (Recorded by the Total_Coded) and homeless death count, which implies that net effect of helpline calls **reduces** homeless death count in Toronto.

@@

modelsummary::modelsummary(
  list(
    "Total Coded Model" = total_coded_model
  ),
  statistic = "mad",
  fmt = 4
)
```

@@

modelsummary::modelsummary(
  list(
    "Referred and Informed Model" = referred_informed_model
  ),
  statistic = "mad",
  fmt = 4
)
```
